Low field depolarization of electronic spins through dipole-dipole coupling

### 2022-04-29 Mes papiers/Low field CR/Low_field_CR.tex
atat

In this letter/article, we characterize the depolarization of the spins observed for dense ensemble of NV centers in zero magnetic field and its potential application for DC magnetometry. While the main mechanism behind the depolarization, the lift in the degeneracy between the four classes of NV centers, is already well studied and can be exploited in a microwave-less vector magnetometry protocol, we found two other depolarization mechanisms specific to the zero-field region which could play an important role in the low-field magnetometry protocol.

@@

Second is the plateau reached for $\Delta \nu \gtrapprox 30\ \rm MHz$. The final $1/T_1^{\rm dd}$ value is about twice as high as that for a spin well aligned with the magnetic field, showing the increased depolarization due to the change of basis.

@@

In order to measure the sensitivity of the measurement, we alternate a small DC field of $\approx 40 \rm G$ every few seconds and take an histogram of the measured fields, as shown in Fig. \ref{magneto} (b) and (c). The histogram is well fitted with gaussians of standard deviation $\sigma=1.5\ \mu \rm T$. The measurement was performed here with an output low-pass filter of time constant $\tau=3\ \rm ms$, which allows us to measure the sensitivity $\eta=\sigma \sqrt{\tau}=82\ \rm{nm}/\sqrt{\rm Hz}$.

>>>>

In this letter/article, we characterize the depolarization of the spins observed for dense ensemble of NV centers in zero magnetic field and its potential application for DC magnetometry. While the main mechanism behind the depolarization, the lift in the degeneracy between the four classes of NV centers, is already well studied and can be exploited in a microwave-less vector magnetometry protocol, we found two other depolarization mechanisms specific to the zero-field region which could play an important role in a low-field magnetometry protocol.

@@

Second is the plateau reached for $\Delta \nu \gtrsim 30\ \rm MHz$. The final $1/T_1^{\rm dd}$ value is about twice as high as that for a spin well aligned with the magnetic field, showing the increased depolarization due to the change of basis.

@@

In order to measure the sensitivity of the measurement, we alternate a small DC field of $\approx 40 \rm G$ every few seconds and take an histogram of the measured fields, as shown in Fig. \ref{magneto} (b) and (c). The histogram is well fitted with gaussians of standard deviation $\sigma=1.5\ \mu \rm T$. The measurement was performed here with an output low-pass filter of time constant $\tau=3\ \rm ms$, which allows us to measure the sensitivity $\eta=\sigma \sqrt{\tau}=82\ \rm{nT}/\sqrt{\rm Hz}$.

### 2022-04-29 Mes papiers/Low field CR/SI/Low_field_CR_SI.tex
atat

\section{Samples}
\section{Experimental Setup}
\section{Data analysis}
\subsection{$T_1$ fitting Protocol}
\subsection{Estimation of fluctuators width}
\section{Les détails qui tuent}
\subsection{Effect of laser polarization}
\subsection{Alignment of B}
La faudrait p-e montrer ce qu'il se passe pour un décalage de quelques degrés. A voir si j'ai déja les plots
\section{Single spin Hamiltonian}
\section{Fluctuator et tout}

>>>>

\section{NV Hamiltonian}
\section{Samples}
\section{Experimental Setup}
\section{Data analysis}
\subsection{$T_1$ fitting Protocol}
\begin{figure}
\includegraphics[width=0.8\textwidth]{Figures_SI/Fig_T1_0B}
\caption{$T_1$ measurement in zero magnetic field with purely exponential and purely stretched exponential fits}
\label{T1_0B}
\end{figure}
\begin{figure}
\includegraphics[width=0.8\textwidth]{Figures_SI/Fig_T1_1x1x1x1}
\caption{$T_1$ measurement in non-zero magnetic field with purely exponential and purely stretched exponential fits}
\label{T1_1x4}
\end{figure}
\begin{figure}
\includegraphics[width=0.45\textwidth]{Figures_SI/fig_alphas}
\caption{Best stretch factor $\beta$ for a $T_1$ fit of the form $f(\tau)=A \exp(-(\frac{\tau}{T_1})^\beta)$}
\label{alphas}
\end{figure}
\subsection{Estimation of fluctuators width}
\section{Les détails qui tuent}
\subsection{Effect of laser polarization}
\begin{figure}
\includegraphics[width=0.9\textwidth]{Figures_SI/fig_Pola}
\caption{Effect of the polarization of the incident laser. (a) Photoluminescence as a function of randomly oriented magnetic field for various polarization angle. (b) Demodulated PL in the same conditions}
\label{Pola}
\end{figure}
\subsection{Alignment of B}
La faudrait p-e montrer ce qu'il se passe pour un décalage de quelques degrés. A voir si j'ai déja les plots
\section{Fluctuator et tout}
\subsection{121 VS 22}
\subsection{100 vs 0B}
